\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-10-26 Paper/Paper.tex
Update D2 table title

\begin{document}
	\vspace{5cm}

	{\fontsize{20pt}{20pt}\selectfont 参赛学生姓名： 潘思齐\\}

	\vspace{0.6cm}
	{\fontsize{20pt}{20pt}\selectfont 中学： 上海市世外中学}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 省份： 上海}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 国家/地区： 中国}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 指导老师姓名： 徐庆林}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 指导老师单位： 上海市世外中学}

	\vspace{1cm}
	{\fontsize{20pt}{20pt}\selectfont 论文题目： }
	{\fontsize{16pt}{16pt}\selectfont Multimodal Abnormity-Aware Model}

	\vspace{0.2cm}
	{\fontsize{16pt}{16pt}\selectfont \hspace{3.7cm} for Ocular Disease Diagnosis}

	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
	\author{Siqi Pan}
	\date{}
	\maketitle

@@

		\begin{table}[H]
		\centering
		\fontsize{9}{12}\selectfont{
			\caption{Test results of Stage D2}
			\label{tb:diagnosis_test}
			\pgfplotstabletypeset[
			multicolumn names,
			col sep=comma,
			columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
			columns/Abnormity/.style={string type, column name=Abnormities},
			columns/Precision/.style={string type, column name=Precision},
			columns/Sensitivity/.style={string type, column name=Sensitivity},
			columns/Specificity/.style={string type, column name=Specificity},
			columns/FOne/.style={string type, column name={F1 Score}},
			columns/AUC/.style={string type, column name=AUC},
			every head row/.style={before row=\toprule, after row=\midrule},
			every last row/.style={ after row=\bottomrule}
			]{Tables/diagnosis2.csv}}
	\end{table}

>>>>

\begin{document}
	\title{\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis}
	\author{Siqi Pan}
	\date{}
	\maketitle

@@

		\begin{table}[H]
		\centering
		\fontsize{9}{12}\selectfont{
			\caption{Test results of Stage D2}
			\label{tb:diagnosis_test}
			\pgfplotstabletypeset[
			multicolumn names,
			col sep=comma,
			columns = {Abnormity, Precision, Sensitivity, Specificity, FOne, AUC},
			columns/Abnormity/.style={string type, column name=Diseases},
			columns/Precision/.style={string type, column name=Precision},
			columns/Sensitivity/.style={string type, column name=Sensitivity},
			columns/Specificity/.style={string type, column name=Specificity},
			columns/FOne/.style={string type, column name={F1 Score}},
			columns/AUC/.style={string type, column name=AUC},
			every head row/.style={before row=\toprule, after row=\midrule},
			every last row/.style={ after row=\bottomrule}
			]{Tables/diagnosis2.csv}}
	\end{table}
